\chapter{Synopsis}
\section{Project Title}
HealthFlow Connect
\section{Internal Guide}
Asst. Prof. Tanuja Pattanshetti 
\section{Problem Statement}
The current paper-based case paper system used in government hospitals in India poses significant challenges in terms of accessibility, efficiency, and accuracy. Healthcare providers struggle with manual data entry processes, limited accessibility to patient records, and fragmented systems for managing patient information. These challenges hinder effective patient management and healthcare delivery, leading to delays, errors, and inefficiencies.

To address these issues, the HealthFlow Connect project aims to digitize the case paper system, leveraging modern technologies to create a comprehensive digital platform for managing patient information and medical records. The project seeks to streamline patient management processes, enhance accessibility to medical records, improve data accuracy, and ensure compliance with data security and privacy regulations.


Addressing these challenges requires the development of a robust, scalable, and user-friendly digital platform that can effectively digitize the case paper system used in government hospitals. The HealthFlow Connect project seeks to tackle these issues by leveraging modern technologies and best practices in software development to create a comprehensive solution that streamlines patient management, enhances accessibility to medical records, improves data accuracy, and ensures compliance with data security and privacy regulations.

\section{Goals and Objectives}

The goals and objectives of the HealthFlow Connect project are as follows:

\subsection{Goals:}

\begin{enumerate}
    \item \textbf{Digitize Patient Records:} Develop a digital platform to replace the paper-based case paper system, enabling the storage and management of patient records in electronic format.
    
    \item \textbf{Streamline Patient Management:} Create a centralized system for patient registration, record updates, case paper generation, and retrieval, to improve efficiency and accuracy in healthcare delivery.
    
    \item \textbf{Enhance Accessibility:} Provide healthcare providers with remote access to patient records, facilitating timely decision-making and improving overall patient care.
    
    \item \textbf{Ensure Data Security and Privacy:} Implement robust security measures to safeguard patient data, ensuring compliance with relevant regulations and standards.
    
    \item \textbf{Integrate Healthcare Services:} Integrate functionalities for doctors, counter staff, lab technicians, pharmacists, and patients into a cohesive platform, promoting collaboration and coordination in healthcare delivery.
\end{enumerate}

\subsection{Objectives:}

\begin{enumerate}
    \item Develop a user-friendly web-based interface for accessing and managing patient records.
    \item Create role-based access control mechanisms to ensure appropriate access to patient records based on user roles.
    \item Implement features for patient registration, record updates, case paper generation, and printing.
    \item Integrate modules for doctors to input diagnoses, prescriptions, and medical histories seamlessly.
    \item Provide functionalities for lab technicians to upload test reports and pharmacists to manage medication records.
\end{enumerate}


\section{Plan of Project Execution}

\begin{table}[htbp]
\centering
\footnotesize
\begin{tabular}{|p{2.5cm}|p{2cm}|p{2cm}|p{2cm}|p{2.5cm}|p{2.5cm}|}
\hline
\textbf{Task} & \textbf{Category} & \textbf{Assigned to} & \textbf{Completed By} & \textbf{Start} & \textbf{Days} \\
\hline
Initiation & & & & & \\
\hline
Characterizing the Issue Domain & High Risk & ALL & ALL & 20-01-2024 & 3 \\
Articulating the Problem Description & Med Risk & Vipul Chaudhari & Vipul Chaudhari & 23-01-2024 & 2 \\
Pinpointing Dependencies & Milestone & Aditya Choudhary & Aditya Choudhary & 25-01-2024 & 3 \\
Project Boundaries & Milestone & Ayush Ambhorkar & Ayush Ambhorkar & 26-01-2024 & 3 \\
Specifying Operational Requirements & High Risk & Aditya Choudhary & Aditya Choudhary & 29-01-2024 & 2 \\
Recognizing Limiting Factors & & Vipul Chaudhari & Vipul Chaudhari & 29-01-2024 & 2 \\
\hline
Planning and Design & & & & & \\
\hline
Gantt Chart Composition & Med Risk & Ayush Ambhorkar & Ayush Ambhorkar & 31-01-2024 & 2 \\
Process Model Recognition & High Risk & Aditya Choudhary, Ayush Ambhorkar & Aditya Choudhary, Ayush Ambhorkar & 02-02-2024 & 1 \\
Tech Infrastructure Identification & High Risk & Aditya Choudhary, Vipul Chaudhari & Aditya Choudhary, Vipul Chaudhari & 03-02-2024 & 3 \\
Software Requirement Specification & High Risk & Vipul Chaudhari, Ayush Ambhorkar & Vipul Chaudhari, Ayush Ambhorkar & 05-02-2024 & 5 \\
Data Flow Diagram & Low Risk & Aditya Choudhary, Vipul Chaudhari & Aditya Choudhary, Vipul Chaudhari & 10-02-2024 & 2 \\
ER Diagram & Low Risk & Ayush Ambhorkar & Ayush Ambhorkar & 10-02-2024 & 2 \\
UML & Med Risk & & & 12-02-2024 & 5 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\centering
\footnotesize
\begin{tabular}{|p{2.5cm}|p{2cm}|p{2cm}|p{2cm}|p{2.5cm}|p{2.5cm}|}
\hline
Backend Development & & & & & \\
\hline
Preliminary Configuration & Low Risk & & & 17-02-2024 & 2 \\
Crafting Routing Structures and Controllers & High Risk & & & 19-02-2024 & 15 \\
Debugging Tool for Evaluation (Postman) & Milestone & & & 05-03-2024 & 3 \\
\hline
Frontend Development & & & & & \\
\hline
Preliminary Arrangements & Low Risk & & & 08-03-2024 & 2 \\
Establishing Communication between Backend and Frontend & High Risk & & & 09-03-2024 & 3 \\
Designing the Foundation of the Web Page & Med Risk & & & 11-03-2024 & 10 \\
Upgrading Design Elements Using Bootstrap & Low Risk & & & 21-03-2024 & 5 \\
Integration of Complete Web Structure & Goal & & & 26-03-2024 & 7 \\
\hline
Testing & & & & & \\
\hline
On site real time testing & Med Risk & & & 02-04-2024 & 3 \\
Feedback analysis & On Track & & & 03-04-2024 & 2 \\
Doing necessary changes & On Track & & & 05-04-2024 & 6 \\
\hline
\end{tabular}
\caption{Project Task Schedule}
\label{tab:tasks}
\end{table}

